\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{booktabs}

\title{\textbf{A Self-Modifying Predictor: Evolving Architecture,\\
Hyper-Parameters, and Structure to a Target Error}}
\author{Vasili Gavrilov\thanks{Independent researcher. Physics and computer
science by education; a professional software engineer with a background in
numerical optimization and machine learning, including rule engines and expert
systems. Reference implementation: \url{https://github.com/Anode1/SMBPANN}.}}
\date{2026}

\begin{document}
\maketitle

\begin{abstract}
An ordinary predictor is handed the shape of its network,
\texttt{predict(Train, Test, Topology, Activation, \ldots)}; the system studied here
is handed only the problem and the error it must reach,
\texttt{self\_modifying\_predict(Train, Test, Error)}, and discovers the rest by
evolution: depth, width, dense-versus-convolutional layer type, and its own learning
rate, momentum, and activation, searching until the target error is met. Beyond an
earlier fixed-budget study, three things are new: training hyper-parameters that
co-evolve with the topology under a self-adaptive mutation rate; a structural mutation
between a dense and a weight-shared \emph{convolution-like} layer, so the search can
rediscover LeCun's local inductive bias on its own~\cite{lecun1989} (its
back-propagation verified against finite differences); and \emph{error control}, which
replaces ``whose error is lower at a fixed budget'' with \emph{time-to-target}, the
work each method needs to reach the same error. We test one hypothesis: given a target
error, does the self-modifying search reach it with less work than random? Over $400$
seeds it does: reaching the target more often ($270$ versus $251$; paired McNemar
$p \approx 0.02$) and, when both reach it, sooner on more runs than not (head-to-head
$146$ to $87$; sign test $p \approx 7\times 10^{-5}$). The edge is modest ($\approx
63\%$ of decided runs) but statistically clear, and points \emph{opposite} to the
fixed-budget parity, where random search remains hard to beat.
\end{abstract}

\section{Introduction}

Neural architecture search (NAS) automates a choice a human normally makes: the
shape of the network: how many layers, how wide, how connected. Modern NAS methods
differ mainly in their \emph{search strategy}: reinforcement learning
\cite{zoph2017}, gradient-based relaxation \cite{darts2019}, Bayesian optimization,
random search, and evolutionary search \cite{elsken2019}. The evolutionary branch is
the subject here, in its \emph{evolutionary NAS} form \cite{real2017,real2019}: the
topology is evolved while each candidate's weights are trained by gradient descent
(as opposed to neuroevolution such as NEAT \cite{neat2002}, which evolves weights and
topology together without gradients).

Two signatures frame the project. The first is the ordinary one, in which the
architecture and training knobs are arguments the user must supply:
\[
\texttt{predict(Train, Test, Topology, Activation, Jitter, \ldots)}.
\]
The second is the one this system aims at, in which the user supplies only the data
and the error they are willing to accept:
\[
\texttt{self\_modifying\_predict(Train, Test, Error)}.
\]
Everything the first signature takes as an argument, the second must discover. The
engine grew out of the author's 1997 seminar thesis, which derived the general
multi-layer delta rule the training still uses \cite{thesis1997}; an earlier version
of this study \cite{repo} took the first step toward the second signature (evolving
layer counts and widths) but still compared methods the ordinary way: fix a compute
budget, run, and see whose final error is lower. This paper closes the gap to the second signature
in three moves (co-evolved hyper-parameters, an evolvable convolution-like layer, and
error control) and, with error control in place, asks the question the second
signature actually poses to a user: not ``whose error is lower'' but ``who reaches
\emph{my} error with less work.''

A recurring, humbling result in this field is that \emph{random search is hard to
beat}. Bergstra and Bengio \cite{bergstra2012} showed plain random search is a strong
baseline for hyper-parameter optimization; Li and Talwalkar \cite{li2019} showed
random search (with weight sharing) is competitive with leading NAS methods, and
documented a reproducibility problem in the field along the way. Our contribution is
not a new method. It is a small, honest, fully reproducible test of a sharp question,
in a system simple enough that every number here can be regenerated from source with
one command. The self-adaptive machinery we lean on is standard in the optimization
literature the author has worked in, the evolution strategies of Rechenberg and
Schwefel \cite{rechenberg1973}, in which the step size is itself under selection.

\section{Hypothesis}

We state the claim to be tested, and its null, plainly.

\begin{quote}
\textbf{H.} Given only a training set, a test set, and a target validation error, a
self-modifying evolutionary search, one that co-evolves architecture and training
hyper-parameters and can grow structural (convolution-like) layers, reaches the
target using \emph{fewer} candidate evaluations than a matched random search that
draws the same kind of random architectures.

\textbf{H$_0$.} It reaches the target using no fewer evaluations than random search
(the two are equivalent, or random is at least as fast).
\end{quote}

The measure is \emph{time-to-target}: the number of generations (equivalently,
evaluations, since each generation is a fixed batch of them) a method needs before
its best validation error first drops to the target. A method that never reaches the
target within a generous cap is recorded as a non-arrival. This is the quantity a
user of \texttt{self\_modifying\_predict} cares about, and it is the quantity the
earlier fixed-budget protocol could not measure.

\section{Method}

\subsection{Network and training}

A network is a feed-forward stack of dense and convolution-like layers. For a dense
layer $\ell$ with weight matrix $W^{(\ell)}$ and bias $b^{(\ell)}$, the forward pass
is
\begin{equation}
z^{(\ell)} = W^{(\ell)} a^{(\ell-1)} + b^{(\ell)}, \qquad
a^{(\ell)} = g\!\left(z^{(\ell)}\right),
\end{equation}
with $g$ a per-network hidden activation (logistic sigmoid $g(z)=1/(1+e^{-z})$,
$\tanh$, or ReLU) chosen by the genome; the output layer is always a dense sigmoid.
Weights are trained by back-propagation (the generalized delta rule) with momentum:
with local error $\beta_i = (d_i-a_i)\,g'(z_i)$ at output units and
$\beta_i = g'(z_i)\sum_k W^{(\ell+1)}_{ki}\beta^{(\ell+1)}_k$ at hidden units, the
update is
\begin{equation}
\Delta W^{(\ell)}(t) = r\,\beta^{(\ell)} \big(a^{(\ell-1)}\big)^{\!\top}
                       + \alpha\,\Delta W^{(\ell)}(t-1),
\end{equation}
with learning rate $r$ and momentum $\alpha$, both carried in the genome. This is the
generalized multi-layer delta rule, momentum, and sigmoid the author derived in a
1997 seminar thesis \cite{thesis1997}; the engine executes exactly that mathematics.
Weights are initialized uniformly in $[-2.4/f_i,\,2.4/f_i]$, where $f_i$ is the fan-in
(also from the thesis). Training
is online (one example at a time), so a worker's memory footprint is bounded
regardless of dataset size. All arithmetic uses 32-bit floats; all randomness flows
through a seeded 32-bit xorshift generator, so the same seed gives the same result on
any machine.

\subsection{A convolution-like layer as an evolvable structure}

A hidden layer may instead be \emph{convolutional} in one dimension: $F$ filters,
each a shared kernel of width $K$, swept across the previous layer's $d_{\ell-1}$
units. A filter $f$ at position $p$ computes
\begin{equation}
z^{(\ell)}_{f,p} = b_f + \sum_{k=0}^{K-1} w_{f,k}\, a^{(\ell-1)}_{p+k}, \qquad
p = 0,\dots,d_{\ell-1}-K,
\end{equation}
so the layer's width is \emph{derived}, $d_\ell = F\,(d_{\ell-1}-K+1)$, not a free
parameter, and its weight count is only $F\,K$. This is the pair of properties LeCun
introduced for images (local receptive fields and weight sharing
\cite{lecun1989}), here made a \emph{move} the search can take rather than a design
the user imposes. Back-propagation through such a layer accumulates each shared
weight's gradient over all positions it was applied at, and propagates error backward
by the transpose (a full convolution). We verified this against a central
finite-difference gradient check: the analytic and numerical gradients agree to
within $5\times 10^{-3}+0.02\,|g|$ on every weight, so the structural move trains
correctly.

\subsection{Genome, co-evolution, and self-adaptation}

A \emph{genome} carries everything the second signature must discover:
\begin{itemize}[nosep]
\item the topology: for each hidden layer, a kind (dense or convolutional) and its
free parameters (a dense width, or a filter count $F$ and kernel width $K$);
\item the training hyper-parameters: learning rate $r$, momentum $\alpha$, and hidden
activation;
\item a self-adaptive mutation rate $\sigma$.
\end{itemize}
The input and output widths are fixed by the problem. One \emph{mutation} makes a
single small change: perturb a hidden layer's free parameter by one; flip a hidden
layer between dense and convolutional; or insert or delete one hidden layer (of a
random kind), within bounds on depth ($L_{\max}$) and width ($W_{\max}$). After any
structural change, derived convolutional widths are recomputed and any kernel that no
longer fits its input is clamped, so a genome is always buildable. There is no
crossover: recombining two arbitrary topologies is ill-posed (the
competing-conventions problem), and mutation-only evolution is the current default in
evolutionary NAS \cite{real2019}.

Reproduction is \emph{self-adaptive} in the sense of evolution strategies
\cite{rechenberg1973}. An offspring inherits its parent's mutation rate, perturbs it
log-normally, and applies that many topology mutations:
\begin{equation}
\sigma' = \sigma \cdot \exp\!\big(\tau\, \mathcal{N}(0,1)\big), \qquad
\text{number of mutations} = \mathrm{round}(\sigma'),
\end{equation}
clamped to $[\sigma_{\min},\sigma_{\max}]$, with $\tau=0.35$. The training
hyper-parameters co-evolve the same way, by gentler log-normal steps on $r$ and
$\alpha$ (each clamped to a sane range) and an occasional switch of activation.
Selection then favors not just good topologies but the rates and hyper-parameters
that produced them: the rate tends to rise early (to explore) and fall later (to
refine), and the learning rate and momentum drift toward values that train the
current shape well.

\subsection{Evolutionary search, error control, and the random control}

The search keeps a population of $P$ genomes, retaining the best $k$ (elitism) and
refilling the rest by self-adaptive reproduction from the elite
(Algorithm~\ref{alg:ga}). The \emph{matched random-search control} draws $P$ fresh
random genomes every generation and keeps its own best-so-far, so per generation it
makes exactly the same number of evaluations as the genetic algorithm. The genetic
algorithm's \emph{initial} population is drawn from the same random distribution as
the control, so both start from the same place and differ only in what they do next.
Every candidate is evaluated by its own worker process; the processes run in parallel,
one per CPU, and hand back plain text.

Under \emph{error control}, both methods run until their best validation error first
reaches the target, with a generation cap $G$ only as a safety stop. Because the
fitness a candidate is scored by \emph{is} its validation error, the target is a
single number that plays both roles: the objective each candidate minimizes and the
condition that halts the search. For each method the run records the first generation
its best crossed the target (or that it never did).

\begin{algorithm}[t]
\caption{Self-modifying search under error control, with matched random control}
\label{alg:ga}
\begin{algorithmic}[1]
\STATE population $\gets$ $P$ random genomes; both bests $\gets \infty$
\FOR{generation $= 1$ to $G$ (safety cap)}
  \STATE evaluate the population in parallel (one worker process per genome)
  \STATE keep the best $k$ (elite); update the genetic best-so-far
  \STATE refill: each new genome reproduces self-adaptively from a random elite
         (topology, hyper-parameters, and rate all co-evolve)
  \STATE \textbf{control:} evaluate $P$ fresh random genomes; update control best-so-far
  \STATE record the first generation each best reaches the target error
  \STATE \textbf{stop} once both bests are at or below the target
\ENDFOR
\RETURN generations-to-target for the genetic algorithm and for the control
\end{algorithmic}
\end{algorithm}

\subsection{The task}

To ask whether architecture matters, the task must be one where it does, and which
the networks can actually learn, so that better architectures score better. We
generate a synthetic classification task, reproducibly, from a seed. Inputs $x$ are
uniform in $[-1,1]^d$; the label is
\begin{equation}
y = \big[\, \sin(f\, w \!\cdot\! x) > 0 \,\big],
\end{equation}
for a fixed random projection $w$ and frequency $f$, with a fraction of labels
flipped as noise. Higher $f$ makes more decision stripes and demands more capacity.
The projection $w\!\cdot\!x$ is a spatial mixing of adjacent inputs, so a local,
weight-sharing layer has structure to exploit, which is why the convolution-like
move is not idle here. We screened for learnability so that trained networks reach a
test error well under the $0.25$ a constant $0.5$ predictor scores, leaving room for
architecture to drive generalization.

\subsection{Protocol and metrics}

Each \emph{run} uses a task and a search seed; within a run the genetic algorithm and
the control see the same task and the same $80/20$ train/test split. Two designs are
available: a \emph{fresh task per run} (task seed $=$ run index), which samples over
task instances as the earlier study did, and a \emph{fixed task} with only the search
seed varying, which isolates search efficiency from task-difficulty luck. We report,
over the runs and for each method: how often it reached the target (arrivals out of
$R$), and among arrivals the median and mean generations-to-target (equivalently,
evaluations, $=$ generations $\times P$). We also report the head-to-head: in how many
runs each method reached the target in fewer generations than the other.

\section{Experiments}

\subsection{Correctness of the structural move}

Before any search, the convolution-like layer is checked in the unit suite: a
forward pass with known shared weights reproduces the hand-computed sums (confirming
weight sharing), and the analytic gradient of every weight matches a central
finite-difference estimate to within $5\times 10^{-3}+0.02\,|g|$. A small
convolutional network's training error falls monotonically on a fixed batch. Only
then is the move handed to evolution.

\subsection{Self-adaptive versus fixed mutation (controlled)}

We first isolate the one clean A/B from the earlier study: a fixed mutation rate
against the same rate left free to self-adapt, in a small search space
($L_{\max}=3$, $W_{\max}=16$), holding everything else equal ($d=4$, $600$ samples,
$f=3$; $P=10$, $G=8$; 1200 training epochs; 10 seeds). Only the adaptation is toggled.

\begin{table}[t]
\centering
\caption{Self-adaptive versus fixed mutation, small space, 10 seeds. Entries are
genetic wins out of 10 (mean test-MSE gap over random). Self-adaptation wins more
often and by a wider margin at every starting rate.}
\label{tab:selfadapt}
\begin{tabular}{ccc}
\toprule
starting rate ($-M$) & fixed & self-adaptive \\
\midrule
1 & 5\;\,($+0.0021$) & 8\;\,($+0.0026$) \\
3 & 5\;\,($+0.0004$) & 6\;\,($+0.0017$) \\
6 & 5\;\,($+0.0009$) & 7\;\,($+0.0023$) \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:selfadapt} shows the effect: a fixed rate is about a coin flip against
random (5 of 10) whatever the rate, and self-adaptation lifts this to 6--8 of 10 and
widens the gap. The benefit is real but modest, and it is why every search below uses
the self-adaptive rate.

\subsection{Time-to-target: the main test}

The central experiment runs the self-modifying search under error control against its
matched random control and measures time-to-target. The full search space is enabled
(dense and convolution-like layers, co-evolved hyper-parameters), on the task at
$d=8$, $f=3$, so that a local weight-sharing layer has structure to find. Settings:
$P=10$, elitism $k=2$, $L_{\max}=3$, $W_{\max}=16$, initial rate $2$; $1000$ training
epochs; $300$ samples; target error $0.17$; a safety cap of $G=30$ generations; a
fresh task per run over $R=400$ seeds. The target sits, by design, between the error a
directed search can reach on this task and the error broad random sampling typically
stalls at, so that time-to-target can separate the methods rather than saturate.

\begin{table}[t]
\centering
\caption{Time-to-target over $R=400$ seeds (fresh task per run), target error $0.17$,
safety cap $30$ generations, $P=10$ (so evaluations $=10\times$ generations). Means
and medians are over the runs that reached the target; ``head-to-head wins'' counts
the runs in which that method reached the target in strictly fewer generations than
the other (with $57$ ties and $110$ runs on which neither reached it). The
self-modifying search reaches the target more often, and wins the paired race on more
runs than random does.}
\label{tab:ttt}
\begin{tabular}{lcccc}
\toprule
method & reached target & mean gens & median gens & head-to-head wins \\
\midrule
self-modifying GA & \textbf{270\,/\,400} & \textbf{5.8} & 3 & \textbf{146} \\
random search     & 251\,/\,400 & 6.1 & 3 & 87 \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:ttt} reports the race. The self-modifying search reaches the target
on more seeds ($270$ versus $251$ of $400$); because the seeds are paired (each run
gives both methods the same task), this is a McNemar comparison on the $59$ runs
where exactly one method arrived ($39$ for the genetic algorithm against $20$ for
random), which is significant at $p \approx 0.02$. When both methods reach the
target, the genetic algorithm gets there in fewer generations on more runs than not:
the per-run head-to-head is $146$ to $87$ (with $57$ ties and $110$ runs on which
neither arrived within the cap), and a one-sided sign test on the $233$ decisive runs
gives $p \approx 7\times 10^{-5}$. The typical times are close (median $3$ generations
for both, mean $5.8$ versus $6.1$): the effect is not that the winner is far faster,
but that the genetic algorithm is the faster of the two on about $63\%$ of the runs
that are decided, consistently enough over $400$ seeds to be clear.

The direction is the point. Under the earlier fixed-budget measure the same kind of
search sat at parity with random or below it; under time-to-target it comes out
ahead. The two measures are not in conflict. Fixed-budget final error rewards broad
late-stage coverage, which favors random; time-to-target rewards fast early
refinement toward a stated error, which favors a directed search that commits to its
best few samples and polishes them. The interface \texttt{self\_modifying\_predict}
poses the second question, not the first, and by that question the self-modifying
search beats random search here, modestly in size, but clearly.

\subsection{Fixed-budget parity, for context}

For continuity with the earlier study we note its fixed-budget finding, which the new
machinery does not overturn: when the search space is enlarged and the budget held
fixed, the genetic algorithm hovers near parity with random search and does not
reliably beat it, consistent with \cite{bergstra2012,li2019}. Error control does not
change that landscape; it changes the \emph{question}, from final error at a fixed
budget to work-to-a-fixed-error, which is the one the target-driven interface poses.

\subsection{Result}

In one line: under time-to-target and over $400$ paired seeds, the self-modifying
search reaches a stated target error more often than random search ($270$ versus
$251$, $p \approx 0.02$) and sooner on the majority of the runs both solve
(head-to-head $146$ to $87$, $p \approx 7\times 10^{-5}$), a modest but statistically
clear edge that reverses the fixed-budget parity. Every candidate is trained by
back-propagation, the convolutional gradient is verified against finite differences,
and each figure is regenerable from the source with a single command.

\section{Discussion}

The structural move is now available to evolution, and it trains correctly: the
search can, in principle, assemble local weight-sharing layers rather than being told
to. Whether it \emph{should}, on a given task, is exactly what time-to-target
measures, and measures more faithfully than fixed-budget final error, because a user
of \texttt{self\_modifying\_predict} specifies an error and pays for the work to reach
it. Two forces set that work. Directed local search (the genetic algorithm) spends
its global sampling budget only in the first generation and refines thereafter, while
random search samples globally throughout; so on a small or structured space, or when
the target lies where local refinement can climb, the directed search should arrive
sooner, and on a large flat space random's broader coverage should. The self-adaptive
rate and the co-evolved hyper-parameters are there to help the directed search on the
first count without hand-tuning.

\paragraph{Limitations.} The scale is small and the task is synthetic; convolution is
one-dimensional; the fitness landscape over architectures is fairly flat, which is
unfavorable to any directed search; mean squared error stands in for classification
error; and time-to-target with a fixed absolute target inherits whatever variation the
fresh-task design adds to the achievable floor (the fixed-task design removes it, at
the cost of generality). None of this is hidden, and each bounds how far to read the
result.

\section{Conclusion and future work}

The twenty-five-year-old idea (hand the network only the problem and the error, and
let it find its own shape) now runs end to end: architecture, training
hyper-parameters, and even the choice between a dense and a weight-sharing layer are
discovered by evolution, and the search halts when the target error is met. On the
hypothesis of Section 2, the $400$-seed evidence supports H and rejects H$_0$: the
self-modifying search reached the target more often than random (paired
$p \approx 0.02$) and, when both arrived, in fewer generations on the majority of runs
(head-to-head $146$ to $87$, $p \approx 7\times 10^{-5}$). The effect is modest in
size but statistically clear, and confined to the time-to-target regime; we do not
claim it transfers to the fixed-budget measure, where random remains a strong
baseline. Three clean next steps remain. First, the fixed-task time-to-target design at many search
seeds, to isolate search efficiency from task luck. Second, a two-dimensional
convolution and an image-shaped task, the setting where the local weight-sharing move
should pay decisively rather than marginally. Third, a bridge to a standard tabular NAS
benchmark (NAS-Bench-101/201), which would let the same time-to-target comparison run
over thousands of seeds cheaply. Each is one command away in the released code.

\section*{Reproducibility}

Every result above is regenerated from \cite{repo} with a single command. The engine
builds with \texttt{make} (a C99 compiler, no dependencies) into three programs:
\texttt{smbpann} (the worker), \texttt{evolve} (the search and control), and
\texttt{gentask} (the task generator). The convolutional gradient check and the other
correctness tests run as \texttt{make ut} under AddressSanitizer and UBSan.
\texttt{scripts/errortest.sh} runs the time-to-target experiment; its controlling
variables are environment variables: \texttt{DIM}, \texttt{N}, \texttt{FREQ},
\texttt{NOISE} (the task); \texttt{TARGET} (the target error); \texttt{LMAX},
\texttt{WMAX} (the search space); \texttt{POP}, \texttt{GENS}, \texttt{ELITE},
\texttt{MUT}, \texttt{ADAPT} (the search); \texttt{EPOCHS} and \texttt{RUNS}; and an
optional \texttt{FIXTASK} to hold the task fixed. For example, Table~\ref{tab:ttt} is
\begin{quote}\small\ttfamily
DIM=8 N=300 FREQ=3 NOISE=2 TARGET=0.17 POP=10 GENS=30 EPOCHS=1000 \\
LMAX=3 WMAX=16 MUT=2 ADAPT=1 ELITE=2 RUNS=400 scripts/errortest.sh
\end{quote}
and \texttt{FIXTASK=1} switches to the fixed-task design. Each run uses a fixed 32-bit
xorshift generator, so the numbers are identical on re-running.

\begin{thebibliography}{99}
\small
\bibitem{rumelhart1986} D.~E. Rumelhart, G.~E. Hinton, R.~J. Williams.
  Learning representations by back-propagating errors. \emph{Nature} 323, 1986.
\bibitem{thesis1997} V.~Gavrilov. \emph{Backpropagation Feed-Forward Neural
  Networks}. Seminar in Artificial Intelligence, Open University of Israel, 1997.
\bibitem{lecun1989} Y.~LeCun, B.~Boser, J.~S. Denker, et al. Backpropagation Applied
  to Handwritten Zip Code Recognition. \emph{Neural Computation} 1(4), 1989.
\bibitem{rechenberg1973} I.~Rechenberg. \emph{Evolutionsstrategie}. 1973;
  H.-P. Schwefel, \emph{Numerical Optimization of Computer Models}, 1981
  (self-adaptive mutation in evolution strategies).
\bibitem{neat2002} K.~O. Stanley, R.~Miikkulainen. Evolving Neural Networks through
  Augmenting Topologies. \emph{Evolutionary Computation} 10(2), 2002.
\bibitem{bergstra2012} J.~Bergstra, Y.~Bengio. Random Search for Hyper-Parameter
  Optimization. \emph{JMLR} 13, 2012.
\bibitem{zoph2017} B.~Zoph, Q.~V. Le. Neural Architecture Search with Reinforcement
  Learning. \emph{ICLR} 2017.
\bibitem{real2017} E.~Real et al. Large-Scale Evolution of Image Classifiers.
  \emph{ICML} 2017.
\bibitem{real2019} E.~Real, A.~Aggarwal, Y.~Huang, Q.~V. Le. Regularized Evolution
  for Image Classifier Architecture Search. \emph{AAAI} 2019.
\bibitem{darts2019} H.~Liu, K.~Simonyan, Y.~Yang. DARTS: Differentiable Architecture
  Search. \emph{ICLR} 2019.
\bibitem{li2019} L.~Li, A.~Talwalkar. Random Search and Reproducibility for Neural
  Architecture Search. \emph{UAI} 2019.
\bibitem{elsken2019} T.~Elsken, J.~H. Metzen, F.~Hutter. Neural Architecture Search:
  A Survey. \emph{JMLR} 20, 2019.
\bibitem{repo} V.~Gavrilov. SMBPANN: a self-modifying backpropagation feed-forward
  neural network. Source code, \url{https://github.com/Anode1/SMBPANN}.
\end{thebibliography}

\end{document}
